NIRCam Calibration Plan

### 2016-12-06 ms.tex
I added info on the MSX calibrator stars spectra and saturation limits.

The primary JWST standards for absolute calibration have been tied to directly calibrated photometric sources through transfers, such as with HST's STIS instrument.
As an independent check on those transfers, NIRCam can be used to observe those directly calibrated sources and transfer from the brightest ($K \sim -1$) sources all the way to the faintest calibrators ($K \sim 16$).
Observing these bright sources (which are bright naked eye stars) with JWST's NIRCam can be achieved with a combination of narrowband filters, small subarray sizes, a Lyot stop pupil mask (19\% transmission) and a neutral density (ND) filter.
The same configuration can then be used on move to fainter sources.

\begin{figure}[!hbtp]
\centering
\includegraphics[width=.4\columnwidth]{msx_nircam_filt.pdf}
\caption{NIRCam filters as compared to the MSX short wavelength filters from \citet{egan1999msxGuide}. F430M best matches the MSX filters.}\label{fig:NCFOV}
\end{figure}

>>>>

The primary JWST standards for absolute calibration have been tied to directly calibrated photometric sources through transfers, such as with HST's STIS instrument.
As an independent check on those transfers, NIRCam can be used to observe those directly calibrated sources and transfer from the brightest ($K \sim -3$) sources all the way to the faintest calibrators ($K \sim 16$).
Figure \ref{fig:msxNCfilterOverlap} shows the MSX filters B1 and B2 as compared to the NIRCam long wavelength filters with some overlap and that the F430M filter most closely matches the MSX bands.
Figure \ref{fig:msxNCfilterOverlap} also shows model spectra from \citet{castelli2004models} for the MSX calibrator stars in \citet{price2004msxCal} near these bandpasses.
The flux has been normalized for each star at 3.6~$\mu$m and then offset for clarity.

Observing these bright sources (which are bright naked eye stars) with JWST's NIRCam can be achieved with a combination of medium-band filters, small subarray sizes, a Lyot stop pupil mask (19\% transmission) and a neutral density (ND) filter.
Using \texttt{webbpsf} and the throughputs in a program called \texttt{pynrc}, we calculate the saturation limits for 2 groups in RAPID mode and find a K-magnitude of saturation of -4.0 for an A1 V star like Sirius and -3.7 for an M3 III star like Gacrux.
This means that the entire sample of stars from \citet{price2004msxCal} are observable in this coronagraphic neutral density mode.

\begin{figure}[!hbtp]
\centering
\includegraphics[width=.55\columnwidth]{msx_nircam_filt.pdf}
\caption{NIRCam filter throughputs (top), MSX filter throughputs \citep{egan1999msxGuide} (middle) and model spectra of MSX calibrator stars (bottom). F430M best matches the MSX filters.}\label{fig:msxNCfilterOverlap}
\end{figure}
